Multiphysics Reactor-core Simulations Using the Improved Quasi-Static Method

### 2018-08-29 doc/Papers/IQS_convergence/IQS_convergence.tex
Including runtime vs error for LRA stuff

The convergence plots show that updating temperature and the PRKE parameters within a macro step has a significant effect on the performance of IQS.  With only one update, IQS was only slightly better than the implicit flux discretization which required about 50\% more time steps than IQS for the same error.  While 5 temperature updates showed a much improved performance for IQS, with the implicit flux discretization required about 400\% more time steps than IQS for the same error level.  \fig{fig:mp} shows that the solution converges with an increase in the number of temperature updates. 
%
Table \ref{tab:ndiff_lra} shows the run time results for the implicit discretization calculations. The number of GMRES linear iterations is included because it is a proportional measure of the computational effort. Tables \ref{tab:iqs_lra} and \ref{tab:iqspc_lra} present the IQS run-times with various numbers of temperature updates.  These run-times are based on total alive time of the execution where the diffusion evaluation is distributed over 24 processors. These run-times show a marginal performance for IQS and superior performance for \iqspc.  Some of the execution times were able to decrease from implicit discretization with the same number of macro steps because IQS is better equipped to resolve the nonlinearity between temperature and amplitude. Furthermore, there seems to be an optimal number of temperature updates to minimize execution time for a given accuracy.
%: IQS only needs one and \iqspc seems to be ideal at 4 updates. This discrepancy in the number of updates shows that an adaptive type implementation of the updates would be ideal, and could enforce a constant error over the transient. 
It is also important to compare the error of implicit discretization with IQS at one update and \iqspc at 4 updates.  IQS shows an error comparable to implicit discretization at $\Delta t = 0.002$, signifying an actual increase in runtime by -34.1\%.  \iqspc shows an error less than implicit discretization at $\Delta t = 0.002$, signifying an actual increase in runtime by $<-34.9\%$. These specific runs are highlighted in Tables \ref{tab:ndiff_lra} - \ref{tab:iqspc_lra}.

@@

>>>>

The convergence plots show that updating temperature and the PRKE parameters within a macro step has a significant effect on the performance of IQS.  With only one update, IQS was only slightly better than the implicit flux discretization which required about 50\% more time steps than IQS for the same error.  While 5 temperature updates showed a much improved performance for IQS, with the implicit flux discretization required about 400\% more time steps than IQS for the same error level.  \fig{fig:mp} shows that the solution converges with an increase in the number of temperature updates. 
%
Table \ref{tab:ndiff_lra} shows the run time results for the implicit discretization calculations. The number of GMRES linear iterations is included because it is a proportional measure of the computational effort. Tables \ref{tab:iqs_lra} and \ref{tab:iqspc_lra} present the IQS run-times with various numbers of temperature updates.  These run-times are based on total alive time of the execution where the diffusion evaluation is distributed over 24 processors. These run-times show a marginal performance for IQS and superior performance for \iqspc.  Some of the execution times were able to decrease from implicit discretization with the same number of macro steps because IQS is better equipped to resolve the nonlinearity between temperature and amplitude. Furthermore, there seems to be an optimal number of temperature updates to minimize execution time for a given accuracy.
%: IQS only needs one and \iqspc seems to be ideal at 4 updates. This discrepancy in the number of updates shows that an adaptive type implementation of the updates would be ideal, and could enforce a constant error over the transient. 
It is also important to compare the error of implicit discretization with IQS at one update and \iqspc at 4 updates.  IQS shows an error comparable to implicit discretization at $\Delta t = 0.002$, signifying an actual increase in runtime by -34.1\%.  \iqspc shows an error less than implicit discretization at $\Delta t = 0.002$, signifying an actual increase in runtime by $<-34.9\%$. These specific runs are highlighted in Tables \ref{tab:ndiff_lra} - \ref{tab:iqspc_lra}.
\fig{fig:lra_rt_vs_err} visualizes the dependence of runtime on error. This figure shows that IQS and IQS P-C generally has a lower runtime for certain error than implicit discretization.

@@

\begin{figure}[htbp!]
\centering
\includegraphics[height=3in]{figures/lra_rt_vs_err.png}
\caption{Runtime vs. error for various number of temperature updates of IQS and IQS P-C, and various time step sizes of Implicit Dis. (lower is better)}
\label{fig:lra_rt_vs_err}
\end{figure}

### 2018-08-29 doc/Papers/IQS_convergence/reviewer_notes.tex
Including runtime vs error for LRA stuff

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx,amsmath, amssymb, amsthm, amsfonts,subcaption}
\usepackage[usenames, dvipsnames]{xcolor}

@@

\item[\fix] \medm{ For the comparison of LRA and TREAT results, the efficiency [how accurate can you be given a fixed execution time or given an accuracy how much execution time do you need] is a very important quantity; the authors discuss it for LRA and TREAT. However, the authors first present results for the errors and then runtime results. Then they try to synthesize efficiency by comparing different cases that have different runtimes and different errors, e.g. page 23 right before Table 5 "IQS-PC shows and error less than implicit discretization at delta t = 0.002, signifying …". I suggest the authors create error vs. execution time plots for different cases and based on these curves discuss efficiency. The manner efficiency is discussed is very confusing and not very useful for the reader. }
\begin{itemize}
\item Is just a plot of error vs. runtime sufficient?
\end{itemize}

>>>>

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx,amsmath, amssymb, amsthm, amsfonts,subcaption}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{float}

@@

\item[\working] \medm{ For the comparison of LRA and TREAT results, the efficiency [how accurate can you be given a fixed execution time or given an accuracy how much execution time do you need] is a very important quantity; the authors discuss it for LRA and TREAT. However, the authors first present results for the errors and then runtime results. Then they try to synthesize efficiency by comparing different cases that have different runtimes and different errors, e.g. page 23 right before Table 5 "IQS-PC shows and error less than implicit discretization at delta t = 0.002, signifying …". I suggest the authors create error vs. execution time plots for different cases and based on these curves discuss efficiency. The manner efficiency is discussed is very confusing and not very useful for the reader. }
\begin{itemize}
\item Fig. 17 visualizes the dependence of runtime on error. This figure shows that IQS and IQS P-C generally has a lower runtime for certain error than implicit discretization.
\item I need help intepreting this result
\end{itemize}
\includegraphics[height=3in]{figures/lra_rt_vs_err.png}
